---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# psychro

A port of the original python
[psychrolib](https://github.com/psychrometrics/psychrolib) library written by D.
Meyer & D. Thevenard, which provides functions to enable the calculation of
psychrometric properties of moist and dry air. The library works in both metric
(SI) and imperial (IP) systems of units.

## Installation

You can install the released version of psychro from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("psychro")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("psychrometrics/psychrolib", subdir = "src/r")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(psychro)

# Calculate the dew point temperature for a dry bulb temperature of 25 C and a relative humidity of 80%
GetTDewPointFromRelHum(25.0, 0.80)
```
